---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# matador

<!-- badges: start -->
<!-- badges: end -->

matador is a simple package intended for plotting and working with matrices. It is intended to help students complete typical linear algebra problems using Rmarkdown. 

## Installation


matador depends on several of the core tidyverse packages, namely purrr, dplyr, and ggplot2, as well as the ggplot2 extension cowplot.

## Examples

Here are a few demonstrations of matador's functionality:

matador makes it easy to visualize two-dimensional linear transformations:

```{r example}
library(matador)
ggplot2::theme_set(ggplot2::theme_minimal())
plot_transform(trans = matrix(c(-1, 1,1, -1), nrow =2))

```

You can do the same for systems of equations:
```{r}
plot_lines(m = matrix(c(-5, 2, 3, 7), nrow =2))
```

Or easily compute arbitrary powers of matrices:
```{r}
mat_pows(matrix(1:9, nrow = 3), 1:5)
```
Or even display the orthogonal decomposition of a matrix:

```{r}
plot_decomposition(square(1, 2, 3, 4))
```

For more details, take a look at the package vignette.

## Acknowledgments

This package could not have been developed without the invaluable [devtools](https://cran.r-project.org/web/packages/devtools/index.html) package, which simplifies and automates the process of package development. 

`make_axes` benefited greatly from [this](https://stackoverflow.com/questions/17753101/center-x-and-y-axis-with-ggplot2) StackOverflow exchange.

Documentation for `vec_helpers` drew on [this](https://stackoverflow.com/questions/15932585/multiple-functions-in-one-rd-file) resource.

`print_eqn` was inspired by
[this](https://stackoverflow.com/questions/30879083/make-r-markdown-code-blocks-into-math-mode)
StackOverflow post.

My primary linear algebra resource was Otto Bretscher's _Linear Algebra with Applications_ (5th ed.).

Professor Joshua Lansky's linear algebra course inspired this package and gave me the knowledge
in linear algebra to complete it.


