---
title: "matador"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{matador}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(matador)
```
Linear algebra is a formidably abstract subject, one that conceals its beauty behind inscrutable matrices.

Matador can help. Born of procrastination on my linear algebra homework, this modest package provides a suite of handy functions for working with and plotting matrices.

Using the `mat2latex` function, you can easily translate matrix computations in R into LaTeX code suitable for Rmarkdown:
```{r mat2latex}
A <- matrix(-1:2, nrow = 2)
B <- matrix(rep(0.5, 4), nrow = 2)
C <- diag(x = 4, nrow = 2)
ABC <- matador::compose_trans(list(C, B, A))
mats <- lapply(list(C, B, A, ABC), matador::mat2latex, sink = TRUE) 
```

\[`r mats[[1]]` `r mats[[2]]` `r mats[[3]]` = `r mats[[4]]`\]


With the `mat_pows` function, you can multiply a matrix by itself as many times as you like:
```{r}

m <- matrix(c(cos(pi / 3), sin(pi / 3), -sin(pi / 3), cos(pi / 3)), nrow =
              2)
mat_pows(m, 1:7)
```
You can solve a system of equations visually using the plot_lines funciton
```{r, fig.align='center', fig.width = 8, fig.height=8}
set.seed(1)

m2 <- matrix(sample(-10:10, 10), nrow = 5)
plot_lines(m = m2, b = sample(0:10, 5))
```
There are also convenience functions to simplify common computations. `square`,
for instance, will automatically construct a square matrix:

```{r}
square(letters[1:9])
```

But the centerpiece is `plot_transform`, a flexible function that plots a set of vectors before and after a linear transformation:
```{r, fig.align='center', fig.width=8, fig.height=8}
plot_transform(trans = list(diag(x=3, nrow =2), 
                            matrix(c(-1, 0, 0, 1), nrow =2), matrix(c(1, 0, 2, 1), nrow = 2)))
```
I hope matador will help you spend less time poring over matrices and more
learning the nuts and bolts of linear algebra.
